Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2021-04-18 manuscript/manuscript.Rmd
Add link to stats notebook
Fix "church" thing

git-repo: https://github.com/andrewheiss/who-cares-about-crackdown

@@

Table \@ref(tab:sample-details) provides a summary of the individual characteristics of survey respondents. Because we limited the sample to people who regularly make charitable contributions, most respondents have a favorable opinion of nonprofits and charities, with more than half reporting a 5 or greater level of trust in charities (on a 7-point scale). Moreover, nearly 90% indicated that it is important to trust charities. Additionally, the majority of respondents volunteer and donate to charity at least once a year and give between \$1–\$999 annually. Most rarely attend church, but feel that religion is important. Respondents are also civically engaged (three quarters voted in the last election) and follow national news closely (70% follow the news daily). Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal–conservative political ideology.

>>>>

code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/who-cares-about-crackdowns/>"

@@

Table \@ref(tab:sample-details) provides a summary of the individual characteristics of survey respondents. Because we limited the sample to people who regularly make charitable contributions, most respondents have a favorable opinion of nonprofits and charities, with more than half reporting a 5 or greater level of trust in charities (on a 7-point scale). Moreover, nearly 90% indicated that it is important to trust charities. Additionally, the majority of respondents volunteer and donate to charity at least once a year and give between \$1–\$999 annually. Most rarely participate in religious services, but feel that religion is important. Respondents are also civically engaged (three quarters voted in the last election) and follow national news closely (70% follow the news daily). Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal–conservative political ideology.
